---
title: "PHC410 (Pharmaceutical Biostatistics)"
subtitle: "Introduction to R"
author: 
  - <put your name here> <your student ID> - <your group>
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document: default
  html_document: default
---
# Activity

1. Import a csv file named `sbs_babyweight.csv` using `read.csv` function. Assign an object called `babyweight` to store the data.

My code:
```{r}
#put your code down here after this line


```


2. List the names of variables in object `babyweight` using `names()`.

My code:
```{r}
#put your code down here after this line

```


3. What is the data structure of `babyweight`?

Answer: <Put your answer here>

My code:
```{r}
#put your code down here after this line

```


4. Use `str()` to observe the followings:

Answer:

    1. The number of observations: <Put your answer here>
    2. The number of variables: <Put your answer here>
    3. The type of variables: <Put your answer here>

My code:
```{r}
#put your code down here after this line

```
&nbsp;

5. Read the description of the data file listed in `sbs_babyweight_desc.txt`. Based on the description, which variables should have the following data types:

Answer:

+ Factor: <Put your answer here>
+ Logical: <Put your answer here>


6. Convert the variables listed in previous question into factor using `as.factor()`. 
    
My code:
```{r}
#put your code down here after this line

```


7. Convert logical variables listed in question 5 using `as.logical()`. 

My code:
```{r}
#put your code down here after this line

```


8. Use `head()` to display the first 10 observations of `babyweight`. What is the baby's gender of the 7th observation? 

Answer: <Put your answer here>

My code:
```{r}
#put your code down here after this line

```


9. Display the last 5 observations of `babyweight` using `tail()`. Was the mother of the last observation diabetic during pregnancy?

Answer: <Put your answer here>

My code:
```{r}
#put your code down here after this line

```

10. Write `babyweight` into a new csv file named `mybabyweight.csv` using `write.csv()`. Do not display the row.names. 

```{r}
#put your code down here after this line

```


    