---
title: "PHC410 (Pharmaceutical Biostatistics)"
subtitle: "Data Analytics 2: Practice"
author: 
  - <put your name here> <your student ID> - <your group>
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document: default
  html_document: default
---


1. Import a csv file `WHO_suicide.csv` from `input` folder to an object `subs_suicide`.
```{r}
#put your code down here after this line
```

2. Convert `country`, `sex`, `age`, and `generation` as factor. _Hint: use as.factor()_
```{r}
#put your code down here after this line

```

3. Create a scatter plot between `gdp` and `suicide_100_population`. Interpret the relationship between the two variables from the graph.

```{r collapse=TRUE}
#put your code down here after this line
```

Interpretation: (put your answer here)


4. Create both stacked and group bar charts that represent the age and the type of generation. Display the legend and set the title of legend as `Age group`. Use `rainbow(6)` as the colours and set a smaller size of x axis labels with `cex.names=0.7`.

```{r collapse=TRUE}
#put your code down here after this line
```

5. Based on your results in question 4, which generation has the highest number of age groups who had attempted suicide?

Answer: (put your answer here)